Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-25 paper/table-data.tex

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129/129 solved aut.\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 796.9 & 111 & 18
\\
&
level 2 &
395 & 24.5 & 1057.1 & 108 & 21
\\
&
level 3 &
393 & 24.9 & 9366.6 & 104 & 25
\\
&
multi &
379 & 27.5 & 11486.6 & 104 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234/234 solved aut.\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 786.3 & 220 & 14
\\
&
level 2 &
569 & 35.5 & 956.2 & 216 & 18
\\
&
level 3 &
562 & 36.3 & 1276.4 & 211 & 23
\\
&
multi &
543 & 38.4 & 2525.3 & 211 & 23
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70/70 solved aut.\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 590.9 & 70 & 0
\\
&
level 2 &
198 & 0.0 & 630.8 & 70 & 0
\\
&
level 3 &
189 & 4.5 & 2127.0 & 63 & 7
\\
&
multi &
189 & 4.5 & 2180.6 & 64 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\90/91 solved aut.\\343 acc.~marks}}
&
level 1 &
328 & 4.4 & 486.5 & 78 & 12
\\
&
level 2 &
330 & 3.8 & 567.0 & 75 & 15
\\
&
level 3 &
322 & 6.1 & 717.0 & 71 & 19
\\
&
multi &
319 & 7.0 & 1622.5 & 72 & 18
\\

>>>>

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\129 automata\\523 acc.~marks}}
&
level 1 &
387 & 26.0 & 796.9 & 111 & 18
\\
&
level 2 &
395 & 24.5 & 1057.1 & 108 & 21
\\
&
level 3 &
393 & 24.9 & 9366.6 & 104 & 25
\\
&
multi &
379 & 27.5 & 11486.6 & 104 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
&
level 1 &
552 & 37.4 & 786.3 & 220 & 14
\\
&
level 2 &
569 & 35.5 & 956.2 & 216 & 18
\\
&
level 3 &
562 & 36.3 & 1276.4 & 211 & 23
\\
&
multi &
543 & 38.4 & 2525.3 & 211 & 23
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\70 automata\\198 acc.~marks}}
&
level 1 &
198 & 0.0 & 590.9 & 70 & 0
\\
&
level 2 &
198 & 0.0 & 630.8 & 70 & 0
\\
&
level 3 &
189 & 4.5 & 2127.0 & 63 & 7
\\
&
multi &
189 & 4.5 & 2180.6 & 64 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\90 automata\\343 acc.~marks}}
&
level 1 &
328 & 4.4 & 486.5 & 78 & 12
\\
&
level 2 &
330 & 3.8 & 567.0 & 75 & 15
\\
&
level 3 &
322 & 6.1 & 717.0 & 71 & 19
\\
&
multi &
319 & 7.0 & 1622.5 & 72 & 18
\\
